\documentclass[11pt]{beamer}
\usetheme{Antibes}

\title{FTech Training}
\subtitle{Using Beamer}
\author{Luc Nguyen}
\institute{HUST}
\date{\today}
\usetheme{Boadilla}

\begin{document}
\begin{frame}
\frametitle{\textbf{HIT SONG PREDICTION}}
\framesubtitle{\textbf{Overview}}
\begin{enumerate}
	\item Description
	\item Regulation
	\item Dataset
	\item Submission form
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{DESCRIPTION}
\begin{itemize}
	\pause\item Build a model to predict whether a given song will become a chart-topping hit.
	\pause\item Hit song prediction is useful to musicians, labels, music vendors.
	\pause\item Timeline : 
	\begin{itemize}
		\pause\item Oct 10, 2019 : Competition starts
		\pause\item Nov 26, 2019 : Deadline for all submissions, including training code, testing code and models.
		\pause\item Nov 27, 2019 : Private test set released.
		\pause\item Nov 28, 2019 : Final solution submitted for private test set.
		\pause\item Dec 09, 2019 : Challenge results announced
		\pause\item Dec, 2019 : Awards Ceremony.
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{REGULATION}
\begin{itemize}
	\pause\item Pre-trained model
	\pause\item Encouraged to open source after the competition
	\pause\item One account per participant
	\pause\item No private sharing outside teams
	\pause\item Term of using data : 
	\pause \begin{itemize}
		\item Only use data for non-commercial research and educational purpose.
		\item Do not distribute the datasets.
%		\item 
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{REGULATION}
\begin{itemize}
	\item Team and product : 
	\begin{itemize}
		\item Maximum 5 mems per team
		\item Submits a maximum of 2 entries per day
		\item Only choose 1 final submissions for judging
	\end{itemize}

\end{itemize}
\end{frame}

\begin{frame}
\frametitle{DATASET}
\begin{itemize}
	\pause\item Three parts of datasets : 
	\begin{itemize}
		\item Training data : 9078 datasets
		\item Public test data : 1118 datasets.
		\item Private test data.
	\end{itemize}
	\pause\item Time restriction : 6 hours on test servers.
\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{DATASET}
	\begin{itemize}
		\item Specific detail :
		\pause \begin{itemize}
			\item Vietnamese song in the audio in .mp3 format
			\item Its metadata : 
			\begin{itemize}
				\item ID
				\item Title
				\item Composer
				\item Singer
				\item Its Zing MP3 rank from 1 to 10 for 6-month period
				\item Released date : 2017 and 2018
			\end{itemize}
		\end{itemize}
		\pause\item Classification : 
		\begin{itemize}
			\item Classical music
			\item Folk music
			\item Pop music 
			\item etc
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{SUBMISSION FORM}
\begin{itemize}
	\pause\item Submit a csv file including ID from the test file and its predicted rank from 1 to 10.
	\pause\item Solution submit : submit training code, testing code and models.
	\pause\item Final results submit : Submit final solution for private test set.
\end{itemize}
\end{frame}
\end{document}