\documentclass[12pt]{article}
\usepackage[left=0.5in,right=0.5in,top=0.0in,bottom=0.5in,
            footskip=0.25in]{geometry}
\usepackage{graphicx,float,hyperref} 
\usepackage{amsmath,amsthm,amssymb,amsfonts,geometry,mathtools}
\usepackage[utf8]{vietnam}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}
 
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
%If you want to title your bold things something different just make another thing exactly like this but replace "problem" with the name of the thing you want, like theorem or lemma or whatever
 
\begin{document}
\title{\textbf{INTERNSHIP TECHNICAL REPORT}}
%\subtitle{asda}
\author{Time Period : Sep 23, 2019 - Oct 21, 2019 \\ Pre-trainee : Nguyễn Văn Lực}
\date{October 22, 2019}
\maketitle
%\begin{abstract}
 %   abstract
%\end{abstract}

%\tableofcontents

\section*{Supervisor : Đinh Thanh Tùng}

\section{Introduction}
\begin{itemize}
	\item I have learnt about the basic Python programming language, some essential libraries such as Numpy, Pandas, Scrapy, Flask.
	\item Tried to implement three basic algorithms (content-based, neighborhood-based collaborative filtering and matrix factorization collaborative filtering) of Recommender System as given on \href{https://machinelearningcoban.com}{\textit{machinelearningcoban.com}}.
	\item Basic knowledge about data analyst on the dataset of the Zalo AI Challenge Hit song prediction.
\end{itemize}

\section{Project and Training Section}
\begin{itemize}
	\item Successfully run three recommender algorithms, source code on \href{https://github.com/nguyenluc99/FTechAI2019/tree/master/RecommendBasic}{\textit{github}}.
	\item Zalo AI Challenge Hit song Prediction data analyst, view pdf on \href{https://drive.google.com/drive/u/0/folders/1WMBcG-PpTjC-7fDdyq_lq4Y9vH18S7XJ}{\textit{driver}} (need permission). 
\end{itemize}
\section{Conclusion and future work}
\subsection{Conclusion}

\begin{itemize}
	\item Understand some basic algorithms of Recommender system, how to implement an Artificial Intelligence program and how it works.
	\item Basic knowledge on data analyst and its role on Artificial Intelligence, Data Science.
\end{itemize}
\subsection{Future work}
\begin{itemize}
	\item Some new algorithms for recommender system such as Linear Regression, Logistic Regression, Overfitting and methods to avoid overfitting.
	\item Apply Linear Regression on the Zalo AI Challenge Hit song Prediction 2019.
	\item Unsupervised Learning and Deep Learning for Recommender System.
\end{itemize}

\section{Personal Opinion}
\begin{itemize}
	\item I am highly grateful if you provide us some international sources, forums to learn more accurately besides Vietnamese sources.
\end{itemize}
\end{document}